Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach

### 2014-06-06 manuscripts/manuscript.Rmd
library at top

@@

plot_sigmas <- ggplot(vary_sigma, aes(noise, value)) + 
  geom_point() + ylab("Net present value") + 
  xlab("Level of growth stochasticity") + theme_bw() 
plot_allees <- ggplot(vary_allee, aes(allee, value)) + 
  geom_point()+ ylab("Net present value") + 
  xlab("Allee threshold stock size") + theme_bw()
cboettigR::multiplot(plot_sigmas, plot_allees, cols=2)

>>>>

library("cboettigR")

@@

plot_sigmas <- ggplot(vary_sigma, aes(noise, value)) + 
  geom_point() + ylab("Net present value") + 
  xlab("Level of growth stochasticity") + theme_bw() 
plot_allees <- ggplot(vary_allee, aes(allee, value)) + 
  geom_point()+ ylab("Net present value") + 
  xlab("Allee threshold stock size") + theme_bw()

multiplot(plot_sigmas, plot_allees, cols=2)
